ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-08-29 reports/paper.tex
nearly at the sending to people stage

%%\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table*}
	\small
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
	\label{tab:water}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllllllll}
		\hline
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
    \hline
    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
	\end{tabular*}
\end{table*}
In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration. After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface. Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough. In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a managageable level) it was not possible to use a Langmuir trough. Instead, small Delrin adsorption troughs were used that did not have controlable barriers. This resulted in no control over the surface pressure of the measurement and therefore it was not possible to co-refine NR contrasts.

@@

To allow for the use of a chemically-consistant model, where the lipid component volumes were allowed to vary, the Python library refnx\cite{Nelson2018} as used. This software allows the inclusion of a custom model from which the parameters fed into the Abel\`{e}s model for the reflection of light at a given number of stratified interfaces,\cite{Abeles1950,Parratt1954} that is typical for reflectometry fitting, are obtained. This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018}

This chemically-consistent model involves two layers; the head layer at the interface with the solvent and tail layer at the interface with the air. The head components have a calculated scattering length, $b_h$, (found as a summation of the number of electrons in the head component multiplied by the classical radius of the electron for XRR or the summation of the neutron scattering lengths for NR), and a component volume, $V_h$. These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$. The tail components also have a calculated scattering length, $b_t$, and a component volume, $V_t$. In this work, the thickness of the tail layer, $d_t$, was found from the length of the carbon tail, $t_t$, and angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
%
\begin{equation}
\label{equ:tl}
d_t = t_t \cos{\theta_t}.
\end{equation}
%
The was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g. it cannot be thicker than the maximum extended length of the lipid tail. The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
%
\begin{equation}
\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
\end{equation}
%
where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains either solvent nor air, e.g. $\phi_t = 0$. To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
%
\begin{equation}
\label{equ:phih}
\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
\end{equation}
%
Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all interfaces, as there is only a single lipid molecule type in each monolayer. Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.

In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across the XRR measurments at four surface concentrations. The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, this based on the understanding that the increasing surface pressure should not significantly influence the head layer thickness. The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given. The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} due to the nature of the monolayer at the surface pressures resulting in the extended, staggered conformation of the chain being likely. For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process.

%
\begin{table}[h]
	\small
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
		\hline
	\end{tabular*}
\end{table}
%
In the second step, the head and tail component volumes, and head layer thickness determined from XRR were used in the refinement of the custom model against the NR measurements. Table \ref{tab:invariant} gives the details of the scattering lengths and SLDs used as invariant parameters in the custom model, while the tail chain lengths were the same as for the XRR. The definition of the head and tail component volumes, and the head thickness allowed the number of variable parameters to be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets.

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data. The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the PDF associated with each parameter. In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations. The use of MCMC sampling allowed for the Bayesian inference of the probability density function for each of the variables and their respective interactions (shown in detail in the ESI). This allowed asymmetric confidence intervals to be found for each of the variable parameters. However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, e.g. they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up. The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
%
\section{Results \& Discussion}
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid. The resulting XRR profiles, associated SLD profiles are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varying parameters for each lipid at the highest surface pressure measured, as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.
%
\begin{table}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}}
	\label{tab:liptab}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
		\hline
	\end{tabular*}
\end{table}
%

@@

\subsection{Effect of compression on the lipid tail component volumes}
It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails is significantly lower in the current measurements than found previously, by other techniques. It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails. However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elavated surface pressure. In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.

In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured. This is based on the assumption that at all four surface pressures, the lipids adopt the same phase and therefore any variation in the structure with surface pressure would manifest as a change in the tail thickness, via the chain tilt angle. It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously. The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} However, DMPG presented a small increase in the tail volume, although this may be due to comparison with a previous measurement at a lower temperature.

\subsection{Solvent effect on lipid head component volumes}
Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids. The three lipids with the PC head component are consistant with values of $\sim330$ \AA$^3$, irregardless of tail component. This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}. Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when compared with either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations.\cite{Kucerka2012} This indicates that there may be some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.

The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic. It has been shown previously that the conformation for the PC component is folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups. A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group. However, such an interaction would be weaker than that observed in the PC component. Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head. This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water. This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group. It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer. Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occuring as a result of interaction with the DES.

\subsection{Refinement of neutron reflectometry}
The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure. The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}. Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the LaTeX ARTICLE template for RSC journals
%Copyright The Royal Society of Chemistry 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table*}
	\small
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
	\label{tab:water}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllllllll}
		\hline
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
    \hline
    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
	\end{tabular*}
\end{table*}
In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration. After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface. Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough. In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough. Instead, small Delrin adsorption troughs were used that did not have controlable barriers. So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.

@@

In this work we would therefore like to use a model that does not assume the molecular volume while remaining physical meaningful. To do this we have allowed the lipid component volumes to vary while constraining the overall system to be self-consistent across multiple different measurements. To do this we have used the Python library refnx\cite{Nelson2018}. This software allows the inclusion of a custom model to be defined, from which parameters feed into the Abel\`{e}s reflectivity model (a model that is widely used to calculate reflectivity \cite{Abeles1950,Parratt1954}). This custom model, along with a series of Jupyter notebooks showing, in full, the analysis performed, can be found in the ESI and is available under CC-BY.\cite{mccluskey_2018}

Our chemically-consistent model is made up of two layers to define the lipid monolayer; the head layer at the interface with the solvent and tail layer at the interface with the air. The head components have a calculated scattering length, $b_h$, (found as a summation of the X-ray or neutron atomic scattering lengths), and a component volume, $V_h$. These head components make up a layer with a given thickness, $d_h$, and roughness, $\sigma_h$, within which some volume fraction of solvent can intercalate, $\phi_h$. The tail components also have a calculated scattering length, $b_t$, roughness, $\sigma_t$, and a component volume, $V_t$. We have defined the thickness of the tail layer, $d_t$, in terms of the maximum (all-trans) length of the carbon tail, $t_t$, and the angle that the chain is tilted by with respect to the interface normal, $\theta_t$,
%
\begin{equation}
\label{equ:tl}
d_t = t_t \cos{\theta_t}.
\end{equation}
%
This was used to impose a chemically-sensible maximum on the thickness of the lipid tail layer, e.g. it cannot be thicker than the maximum extended length of the lipid tail. The scattering length density (SLD) of the tail and head layers used in the Abel\`{e}s model can therefore be found as follows,
%
\begin{equation}
\text{SLD}_i = \frac{b_i}{V_i}(1 - \phi_i) + \text{SLD}_{s}(\phi_i),
\end{equation}
%
where, $\text{SLD}_{s}$ is the scattering length density of the subphase (DES), and $i$ indicates either the tail or head layer; it is assumed that the tail layer contains neither solvent nor air, e.g. $\phi_t = 0$. To ensure that the number density of head components and pairs of tail components is the same, the following constraint was included in the model,\cite{Braun2017}
%
\begin{equation}
\label{equ:phih}
\phi_h =  1 - \bigg(\frac{d_tV_h}{V_td_h}\bigg).
\end{equation}
%
Based on the work of Campbell \emph{et al.},\cite{Campbell2018} a single value for the interfacial roughness was fitted for all of the interfaces, including the subphase (i.e. $\sigma_h$ = $\sigma_t$ = $\sigma_s$), as there is only a single lipid molecule type in each monolayer. Therefore, any capillary wave roughness at the air-DES interface is carried equally through the layers.

In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations. The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, an assumption that is based on our belief that increasing surface pressure should not significantly influence the head layer thickness. The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given. The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied. For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process. Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.

%
\begin{table}[h]
	\small
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
		\hline
	\end{tabular*}
\end{table}
%
In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements. This approach means that the number of variable parameters to fir the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets. Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data. The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the PDF associated with each parameter. In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations. The use of MCMC sampling allowed for the Bayesian inference of the probability density function for each of the variables and their respective interactions (shown in detail in the ESI). This allowed asymmetric confidence intervals to be found for each of the variable parameters. However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e. they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up. The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
%
\section{Results \& Discussion}
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid. The resulting XRR profiles, associated SLD profiles are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varying parameters for each lipid at the highest surface pressure measured, as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.

The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure. The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}. Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
%
\begin{table}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}}
	\label{tab:liptab}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
		\hline
	\end{tabular*}
\end{table}
%

@@

\subsection{Effect of compression on the lipid tail component volumes}
It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques. It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails. However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure. In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.

In this work, a single tail component volume was fitted to each lipid for all four surface pressures that were measured. This is based on the assumption, that at all four surface pressures, the lipids adopt the same phase (as discussed in the ESI) and therefore any variation in the structure with surface pressure would manifest only as a change in the tail thickness, via the chain tilt angle. It is clear when comparing Tables \ref{tab:water} and \ref{tab:liptab} that some of the tail component volumes are also reduced in the current XRR measurements compared to those determined previously. The reduction was found to be between 8-12 \% for DPPC, DMPC and DLPC when compared with literature sources at 24-30 $^\circ$C, this is in good agreement with the maximum compression percentage of 15 \% noted by Small and coworkers.\cite{Small1984} DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature. Notably our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.

\subsection{Solvent effect on lipid head component volumes}
Figure \ref{fig:lipresults} shows the PDFs determined for the head component volume for each of the four lipids. The three lipids with the PC head component are consistent with values of $\sim330$ \AA$^3$, regardless of tail component. This agrees well with the values found for the same head component in water, shown in Table \ref{tab:water}. Interestingly, the component volume for the PG head is similar to that for the PC head with a value of \input{../output/dmpg/vh.txt}\AA$^3$, whereas it is considered to be smaller in water when compared with either DMPG using differential vibrating tube densimetry\cite{Pan2012} or POPG using molecular dynamics simulations.\cite{Kucerka2012} This indicates that there may be some affect arising from the solvation in DES causing an apparent increase in the PG component volume when compared with water.

The major difference between the two head components is the fact PG component is negatively charged whereas the PC component is zwitterionic. It has been shown previously that the conformation for the PC component is folded in water,\cite{Gilliams2016} due to the interaction between the positively-charged ammonium and the negatively-charged phosphate groups. A similar structure may occur for the PG component, with the interaction between the partially postively-charged alcoholic hydrogen atoms and the negatively-charged phosphate group. However, such an interaction would be weaker than that observed in the PC component. Therefore, this observed increase found for the PG component volume in DES when compared with water may be due to the unfolding of the PG head. This unfolding would be made possible by the charged nature of the solvent providing a greater screening effect for the PG head than are present in water. This effect may not be observed for the PC component due to the greater strength of the folding arising from the formally-charged nature of the ammonium group. It would be anticipated that this unfolding would result in an increase in the thickness of the lipid head layer. Previously, DPPG has been reported to have a head layer thickness of $10.3\pm0.4$ \AA\ at 22 mNn$^{-1}$ from neutron reflectometry measurements,\cite{Clifton2012} which it slightly less than the \input{../output/dmpg/head.txt} \AA\ determined in the current work, further suggesting that the unfolding of the PG head component may be occurring as a result of interaction with the DES.
